---
title: "covid-19 data retrieve, and visualization using leaflet"
date: "`r format(Sys.time(), '%Y年%m月%d日')`"
output: 
  - github_document
---
  
[![Build Status](https://travis-ci.com/yiluheihei/ncovmap.svg?branch=master)](https://travis-ci.com/yiluheihei/ncovmap)
[![License: CC BY 4.0](https://img.shields.io/badge/License-CC%20BY%204.0-lightgrey.svg)](https://creativecommons.org/licenses/by/4.0/)

English | [简体中文](README.md)

```{r set}
knitr::opts_chunk$set(
  fig.path = "man/figures/",
  message = FALSE
)
```

## Data source

- raw data from [DXY-COVID-19-Data](https://github.com/BlankerL/DXY-COVID-19-Data)
- preprocessed data from [nCoV-2019-Data](https://github.com/yiluheihei/nCoV-2019-Data)

## Installation

```{r eval=FALSE}
if (!require(remotes)) install.packages("remotes")
if (!require(ncovmap)) remotes::install_github("yiluheihei/ncovmap")
```

Feature:

- `get_ncov2()`: retrieve latest or time-series data of covid-2019 
- `plot_china_map()`: plot on china map
- `plot_province_map()`: plot on province map of china
- `plot_world_map()`: plot on world map
- `plot_foreign_map()`: plot on japan, korea, italy or iran map

```{r load-ncovmap,message=FALSE}
library(ncovmap)
library(leafletCN)
library(magrittr) # for pipe
```

## How to use

### Data retrieve

```{r data, message=FALSE}
# latest data
ncov <- get_ncov2(method = "api")
# ncov class inherit from data.frame
ncov
data.frame(ncov) %>%
  head()
```

### Data subset

```{r subset}
# china data
china <- ncov['china']
china
# Hubei province of china
hubei <- ncov['Hubei']
hubei
# Beijing
beijing <- ncov['Beijing']
# world data
world <- ncov['world']
world

data.frame(world) %>% 
  head()
```

### china map

```{r china-map}
plot_china_map(china, legend_position = "bottomleft")
```

### province map of china

Hubei province

```{r hubei-map}
plot_province_map(
  hubei, 
  "Hubei", 
  bins = c(0, 100, 200, 500, 1000, 10000)
)
```

Beijing

```{r beijing-map}
plot_province_map(
  beijing,
  "Beijing", 
  bins = c(0, 10, 50, 100)
)
```

### world map

```{r world-map}
plot_world_map(world, legend_position = "bottomleft")
```

### korea map

```{r korea-map}
korea_ncov <- get_foreign_ncov("韩国")
plot_foreign_map(korea_ncov, "korea")
```

### japan map

```{r jp-map}
jp_ncov <- get_foreign_ncov("日本")
plot_foreign_map(jp_ncov, "japan")
```

### iran map

```{r iran-map}
iran_ncov <- get_foreign_ncov("伊朗")
plot_foreign_map(iran_ncov, "iran")
```

### italy map 

```{r italy-map}
italy_ncov <- get_foreign_ncov("意大利")
plot_foreign_map(italy_ncov, "italy")
```

## plot multiple maps

```{r four-country-map,eval=FALSE}
## not run
foreign_countries <- c("韩国", "伊朗", "日本", "意大利")
names(foreign_countries) <- c("korea", "iran", "japan", "italy")
htmltools::tagList(purrr::imap(
  foreign_countries, 
  ~ get_foreign_ncov(.x) %>% 
    plot_foreign_map(.y)
))
```

## Acknowlegement

- [DXY-COVID-19-CrawlerAPI](https://github.com/BlankerL/DXY-COVID-19-Crawler)
- [DXY-COVID-19-Data](https://github.com/BlankerL/DXY-COVID-19-Data)

